---
title: "package for all of functions from class"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package for all of functions from class}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753CERV24)
```

# Introduction
This package was created in my journey along MATH 4753. It contains functions that showcase various topics we learned throughout the semester. Below I will demonstrate some of those functions 

## Function 1: myncurve()
```{r}
myncurve(4,2,6)
```

The myncurve() function returns a list of the mean, variance, and the area of probability. Additionally it also produces the plot of the probability area. It is equivalent to using the pnorm() function. 

## Function 2: myclt()
```{r}
myclt(n=5, iter=1000)
```

The myclt() function produces a histogram of the sums of the given sample size and number of iterations. It creates a histogram as well to represent these values.

## Function 3: myplot()
```{r}
myplot(5)
```
The function myplot() produces a number given x for the plot 0.86089580 + 1.46959217(x) - 0.02745726(x^2)



## Function 4: ntickets()
```{r}
ntickets(N=400, gamma=0.02, p=0.95)
```
The function ntickets() is the function I produced from project1. It creates a for plot for the discrete probability function and a plot for the continuous function. Then returns a list of the optimal number of tickets to be sold for each case.s

